There once was a grid at ol' Carkeek

### 2015-10-06 Manuscript/carkeek_grid.tex
added description of basics of model

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).
We constructed the following mathematical model (\ref{my_equation_label}) to better understand the concept:
% using '\ref{something}' in the text will refer to any object (e.g. figure, equation, table) which contains the corresponding '\label{something}'
% Note that you need to run latex a few times to get it to register numbers correctly

\begin{equation}\label{my_equation_label}
	Y = 2a + 2a
\end{equation}

Where $a$ represents an apple.

>>>>

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).

We modeled the counts of DNA sequences ($Z$) from each of a given taxon $i$, in each replicate PCR $j$, from each replicate of a given location $k$ (hence, $Z_{ijk}$), as though they are ?(proportional to/drawn from)? a Poisson distribution. Poisson distributions are described by one and only one parameter, their mean; in this case the mean is given by an exponential function $e^\lambda$. % WHY IS IT EXPONENTIATED? COUNTS?
Thus,
\begin{equation}\label{some_cool_eqn_name}
	Z_{ijk} \sim Poisson(e^{\lambda_{ijk}})
\end{equation}

In turn, we further assume this parameter $\lambda$ is linearly proportional to a suite of taxon-, pcr-, and site- specific parameters describing the variance associated with each sub-process linking the amount of DNA ($Y$) of a given taxon $i$ at a given location $k$ in a DNA extract (hence $Y_{ik}$):

\begin{equation}\label{GLM}
	\lambda_{ijk} = \beta_0 + \beta_i + \eta_{ijk} + \epsilon_{ijk}
\end{equation}

Where $\beta_0$ is a general intercept across all taxa, $\beta_i$ is a fixed effect accounting for the variance associated with taxon $i$, and $\eta_{ijk}$ and $\epsilon_{ijk}$ are random effects of variance resulting from the processes associated with PCR and spatial location, respectively.

%We constructed the following mathematical model (\ref{my_equation_label}) to better understand the concept:
% using '\ref{something}' in the text will refer to any object (e.g. figure, equation, table) which contains the corresponding '\label{something}'
% Note that you need to run latex a few times to get it to register numbers correctly

%\begin{equation}\label{my_equation_label}
%	Y = 2a + 2a
%\end{equation}
%
%Where $a$ represents an apple.
